%\documentclass[lettersize,journal]{IEEEtran}
\documentclass[sigconf,screen,review]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{outlines}
\input{preamble.tex}
\newcommand{\ApproachName}{{\sc Imhotep}}
\newcommand{\simhotep}{$S_{Imhotep}$}
\newcommand{\timhotep}{$T_{Imhotep}$}
\newcommand{\CaseStudy}{Kromaia}

\acmBooktitle{Companion Proceedings of the 32nd ACM Symposium on the Foundations of Software Engineering (FSE '24), July 15--19, 2024, Porto de Galinhas, Brazil}

\begin{document}

\title{Automated Software Transplantation on Procedural Content Generation}
%\author{Mar Zamorano, Carlos Cetina, Federica Sarro}

\author{Mar Zamorano}
\email{maria.lopez.20@ucl.ac.uk}
%\email{mzamorano@usj.es}
\affiliation{%
  \institution{University College London}
  \city{London}
  \country{UK}
}
% \affiliation{%
%   \institution{Universidad San Jorge}
%   \city{Zaragoza}
%   \country{Spain}
% }

\author{Carlos Cetina}
\email{ccetina@usj.es}
% \affiliation{%
%   \institution{University College London}
%   \city{London}
%   \country{UK}
% }
\affiliation{%
  \institution{Universidad San Jorge}
  \city{Zaragoza}
  \country{Spain}
}

\author{Federica Sarro}
\email{f.sarro@ucl.ac.uk}
\affiliation{%
  \institution{University College London}
  \city{London}
  \country{UK}
}

\renewcommand{\shortauthors}{Zamorano et al.}

\begin{abstract}
Software transplantation has been proposed for generating new piece of software by reusing existing parts from a given piece of software (i.e., host) to enhance other parts of a same software or different software (i.e., donor).
In this paper, we propose the first use of transplantation for automatically generating video-game content, dubbed \textit{Procedural Content Transplantation}, which represents a new research angle with respect the existing Procedural Content Generation (PCG) field, which aims for the (semi) automatic generation of new content within video games. 
While current PCG proposals generally give developers limited control over the content generation process, our proposed approach to PCT, dubbed  \ApproachName{}, aims at putting the developers back into the driver seat by allowing the developer to choose \textit{what} to transplant (i.e., the organ from a donor) and \textit{where} (i.e., the host that will receive the organ), while  \ApproachName{} automatically searches  for an appropriate solution to integrate the organ into the host. Such a search is performed by using an evolutionary algorithm guided by simulation-based fitness function, which is also novel w.r.t previous transplantation work generally guided by test-suite compliance.
We empirically evaluate \ApproachName{} in an industrial case study performed in collaboration with the developers of the commercial game \CaseStudy{}. We benchmark the performance of  \ApproachName{}  with respect to a state-of-the-art approach in search-based PCG (SBPCG), as well as a variant of \ApproachName{}  itself guided by a test-suite-based fitness function.
By using \ApproachName{},  \CaseStudy{} developers were able to successfully transplant a total of 129 distinct organs taken from the scenarios of \CaseStudy{} into five different hosts, therefore generating new non-playable characters for this game. We provide empirical evidence showing that the simulation-based \ApproachName produces results that are 1.5 times superior to those of its test-suite-based variant, and 2.5 times superior to the SBPCG benchmark.
%The statistical analysis confirms the significance of these differences and highlights the substantial magnitude of improvement. 
Furthermore, we also unveil organ interactions that have not been  identified previously in the literature. Finally, a focus group with game developers indicated their satisfaction with the generated content and willingness to use it in their game development activity.
\end{abstract}

% \begin{IEEEkeywords}
% Automated Software Transplantation, Auto-transplantation, Procedural Content Generation, Search-Based Software Engineering, Model-Driven Engineering
% \end{IEEEkeywords}

%\keywords{Automated Software Transplantation, Auto-transplantation, Procedural Content Generation, Search-Based Software Engineering, Model-Driven Engineering}


\maketitle

\input{Text/1_Introduction}
\input{Text/2_Background}
\input{Text/3_Approach}
\input{Text/4_Evaluation}
\input{Text/5_Results}
\input{Text/6_Discussion}
\input{Text/7_Threats}
\input{Text/8_RelatedWork}
\input{Text/9_Conclusion}

\begin{acks}
    Work supported by National R+D+i Plan PID2021-128695OB-100, José Castillejo CAS18/00272, ERC grant 741278.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
%\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
